---
title: "Get Started"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(webhoser)
key <- readRDS("../key.rds")
```

Let's walk you through `webhoser` with a simple use case: we'll get articles and blog posts about the R programming language. But first, we need to authenticate, head over to [webhose.io](https://webhose.io/) if you do not have an account yet. The aforementioned account will give you an _API Key_, this is what you will use in the function below.

```{r, eval=FALSE}
(token <- wh_token("xXX-x0X0xX0X-00X"))
```

```{r, eval=TRUE, echo=FALSE}
(token <- wh_token(key))
```

Great, now that we have a token, we can fetch some articles.

```{r}
token %>% 
  wh_news(q = '"R programming language" OR "rstats" is_first:true language:english site_type:news') -> rstats
```

[webhose.io](https://webhose.io/) gives 1,000 results per month for free, `wh_news` and `wh_broadcasts` print the number of queries left by default.

We can paginate through the results if we want more data; let's get five more pages.

```{r}
rstats %>% 
  wh_paginate(5) -> rstats_pagingated

class(rstats_pagingated)
```

So we fetched one page of results then using that object we paginated through 5 more pages. However, this returns an object of class `webhoser`. 

```{r}
rstats_df <- wh_collect(rstats_pagingated)
class(rstats_df)
```

The above functions can be summed up to

```{r, eval=FALSE}
rstats <- token %>% 
  wh_news(q = '"R programming language" OR "rstats" is_first:true language:english site_type:news') %>% 
  wh_paginate(5) %>% 
  wh_collect()
```

```{r, eval=TRUE, echo=FALSE}
rstats <- rstats_df
```